---
title       : BMI Index Caculation
subtitle    : and Implementation in Shiny
author      : KS
job         : Data Sci
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax, shiny, interactive]            
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## The BMI Index and Formula

1. The BMI stands for body mass index.
2. It is a measure of relative weight based on an individual's mass and height.
3. Its mathematical formula is: $$\frac{Weight}{Height^2}$$
4. If your BMI <= 18.5, you are underweight; if your BMI >= 25, you are overweight; if your BMI is in between, you are normal. 

---
## Example 1
Let is compute two BMI Cases in R.
Case 1: weight is 80, height is 1.75 m

```{r echo =TRUE}
weight <-80
height <- 1.75
BMI <- weight/(height^2)
print(sprintf("Your BMI is: %.2f", BMI))
```


---
## Example 2
Case 2: weight is 90, height is 1.70 m

```{r echo = TRUE}
weight <-90
height <- 1.70
BMI <- weight/(height^2)
if (BMI > 25) {
    print(sprintf("Your BMI is: %.2f", BMI))
    print("You are overweight!")
    
}
```


--- &interactive

## Implemented in Shiny
The following is the actual interactive application in shiny.
```{r,  opts.label = 'shiny', echo= FALSE}
slidifyUI(
    
    pageWithSidebar(
        h3("BMI Caculator"),
        sidebarPanel(
            numericInput('Weight', 'Weight in kg', 80, min = 20, max = 300, step = 1),
            numericInput('Height', 'Height in meter', 1.75, min = 0, max = 3, step = 0.01),
            submitButton('Submit')
            
        ),
        
        
        mainPanel(
            h2('                   '),
            h2('                   '),
            h3('Results of Your BMI'),
            h5('Your Weight entered in Pounds:'),
            verbatimTextOutput("WeightValue"),
            h5('Your Height entered in Inches:'),
            verbatimTextOutput("HeightValue"),
            h5('Your BMI is:'),
            verbatimTextOutput("BMI"),
            h5('Your BMI category is:'),
            verbatimTextOutput("BMI_message")
        )
    )
)

```
-----

